The Role of Video Data Sharing in Advancing Education Policy and Practice

### 2015-04-30 2015-06-01-nsf-ed-workshop/paper.tex
full outline

\documentclass[a4paper,man,natbib]{apa6}

@@

Your introduction goes here! Some examples of commonly used commands and features are listed below, to help you get started.

If you have a question, please use the support box in the bottom right of the screen to get in touch.

\section{Promise of Video Data Sharing}
\label{sec:examples}

\subsection{Sections}

Use section and subsection commands to organize your document. \LaTeX{} handles all the formatting and numbering automatically. Use ref and label commands for cross-references.

\subsection{Comments}

You can add inline TODO comments with the todonotes package, like this:
\todo[inline, color=green!40]{This is an inline comment.}

\subsection{References}

\subsection{Tables and Figures}

\subsection{Lists}

You can make lists with automatic numbering \dots

\begin{enumerate}
\item Like this,
\item and like this.
\end{enumerate}
\dots or bullet points \dots
\begin{itemize}
\item Like this,
\item and like this.
\end{itemize}

We hope you find write\LaTeX\ useful, and please let us know if you have any feedback using the help menu above.

>>>>

\documentclass[letterpaper,man,natbib]{apa6}

@@

Video is a uniquely rich medium for capturing in real time the interactions that go on in classroom, laboratory, and informal learning settings.

\section{The Promise of Video Data Sharing}

\subsection{Video is Uniquely Rich}

\subsection{Video Uses in Education}

\section{The Challenges of Video Data Sharing}

\subsection{Technical}

\subsubsection{Online Video Sharing}

\begin{itemize}
\item Size of files
\item Storage/streaming
\item Formats/transcoding
\item Preservation
\end{itemize}

\todo[inline, color=green!40]{Grab text from other papers?}

\subsubsection{Tools for Coding Video}

Human coders evaluate, apply text-based labels to videos using a wide-range of commercial and academic coding tools: Transana, StudioCode, V-code, MaxQDA, Noldus Observer, Mangold Interact, Datavyu.
No standard data format for coding tools.
Some offer web/cloud based storage (e.g., Transana, V-code), but otherwise coded data may not be easily shared within tools, much less between them.
With few exceptions, machine learning has not been applied to video data coding.

\subsection{Ethics and Privacy}

\subsection{Data Management}

\subsection{Changing Community Practices}

\section{Databrary.org}

\subsection{System Design}

\subsection{Policies for Safe, Secure, \& Sharing}

\subsection{Managing Data for Sharing}

\section{Conclusion}
